---
title: "Table formatting and coloring"
output: html_notebook
---

The goal here is to get at nicly formatted table with color which depent on the numbers.

The link to the used data: <br>
https://www.kaggle.com/szrlee/stock-time-series-20050101-to-20171231 <br>
GOOGL_2006-01-01_to_2018-01-01.csv <br>
If it downloads as a xls file, just rename it.

First we need to add the libraries

```{r eval=FALSE, include=FALSE}
#if you haven't installed the packages
install.packages("readr")
install.packages("tidyr")
install.packages("formattable")
install.packages("DT")
```


```{r}
#implementeren van libraries
library("readr")
library("tidyr")
library("formattable")
library("DT")
```

```{r}
#Data invoegen
numberdata <- read_csv("D:/R lessons/Selfmade exersizes/numberdata.csv")
#if there are NA's, this will remove it
numberdata <- drop_na(numberdata)
```

Now we have our data-set, we can use it for analysis and such.

The first package I wanted to use here was formatteble.
So lets import it and see what we can do.

```{r eval=FALSE, include=FALSE}
#lets first see the difference in showing the basic data
head(numberdata)
formattable(numberdata)
```

```{r}
#I like the 'formattable(numberdata)' better, however it will show all data (thats why I won't show it in this markdown)
# resolve this there is DT (package)
head(numberdata)
as.datatable(formattable(numberdata))
```

Woops, a little to much data.

Lets try to get some color in the data.

```{r}
as.datatable(formattable(numberdata, list(area(col = 2:5) ~ color_tile("transparent", "red"))))
```

Seems to work, but I would like some more colors.
Lets try again.

```{r}
as.datatable(formattable(numberdata, lapply(1:nrow(numberdata), function(row) {area(row, col = 2:5) ~ color_tile("red", "green")})))
```

That's what I wanted
