---
title: "Apriori, Sequential patterns and outliers"
output:
  html_document:
    df_print: paged
---
<p>
To be sure I have clean data, I will use the datasets from R base.

I found this sheet about machine learning: https://cran.r-project.org/doc/contrib/YanchangZhao-refcard-data-mining.pdf <br>
So for now I limed myself to this sheets recommendations.

</p>

Lets start

Libraries:
```{r eval=FALSE, include=FALSE}
#instal
install.packages("arules")
install.packages("arulesViz")
install.packages("TraMineR")
install.packages("outliers")

```


```{r}
#add
library("arules", lib.loc="~/R/R-3.5.1/library")
library("TraMineR", lib.loc="~/R/R-3.5.1/library")
library("outliers", lib.loc="~/R/R-3.5.1/library")
library("arulesViz", lib.loc="~/R/R-3.5.1/library")

```

Now lets start trying things.

```{r}
#Apriori
data("Groceries")
str(Groceries)
head(Groceries@itemInfo, n=12)
summary(Groceries)
rules <- apriori(Groceries, parameter = list(supp = 0.001, conf = 0.80))
inspect(rules[1:10])
```

```{r}
plot(rules[1:20],
     method = "graph",
     control = list(type = "items"))

plot(rules[1:20],
     method = "paracoord",
     control = list(reorder = TRUE))
```

Lets say this: it does look interesting, but I have no idea what I'm doing or looking at. I'm going to the next machine learning method. This will be something for in the future.<br>

Also, I'm not gone use the arules-package anymore.

```{r}
#Sequential patterns
data("actcal.tse")
actcal.eseq <- seqecreate(actcal.tse)

fsubseq <- seqefsub(actcal.eseq, min.support=25)
fsubseq <- seqefsub(actcal.eseq, pmin.support=0.01)

fsubseq[1:10]

fsubseq <- seqefsub(actcal.eseq, min.support=10, constraint=seqeconstraint(age.min=6, age.max=9))

fsubseq[1:10]

fsubseq <- seqefsub(actcal.eseq, min.support=10, constraint=seqeconstraint(max.gap=2, window.size=6))

fsubseq[1:20]

```

At least I understand what I'm doing. Lets try to plot some things.

```{r}
data("actcal.tse")
actcal.eseq <- seqecreate(actcal.tse)

fsubseq <- seqefsub(actcal.eseq, min.support=25)
fsubseq <- seqefsub(actcal.eseq, pmin.support=0.01)

fsubseq[1:10]

fsubseq <- seqefsub(actcal.eseq, min.support=10, constraint=seqeconstraint(age.min=6, age.max=9))

fsubseq[1:10]

fsubseq <- seqefsub(actcal.eseq, min.support=10, constraint=seqeconstraint(max.gap=2, window.size=6))

fsubseq[1:20]

plot(fsubseq[["data"]][["Support"]], fsubseq[["data"]][["Count"]])
```

I can't combine the subseq and the data-table to one. <br>
It looks like I can get outliers from this data. Lets try

```{r}
dat <- fsubseq$data
outlier(dat)
mean(dat$Support)
mean(dat$Count)

#remove outliers
dato <- rm.outlier(dat)
outlier(dato)
mean(dato$Support)
mean(dato$Count)

while(outlier(dato$Count) > mean(dato$Count) + 50){
  dato <- rm.outlier(dato)
}

plot(dato$Support, dato$Count)
```

That would work with real data. <br>

On to the next document.
