---
title: "Table formatting and coloring"
output:
  html_document:
    df_print: paged
---

The goal here is to get at nicely formatted table with color which depend on the numbers.

The link to the used data: <br>
https://www.kaggle.com/szrlee/stock-time-series-20050101-to-20171231 <br>
GOOGL_2006-01-01_to_2018-01-01.csv <br>
If it downloads as a xls file, just rename it.

First we need to add the libraries

```{r eval=FALSE, include=FALSE}
#if you haven't installed the packages
install.packages("readr")
install.packages("tidyr")
install.packages("formattable")
install.packages("DT")
```


```{r}
#implementeren van libraries
library("readr", lib.loc="~/R/R-3.5.1/library")
library("tidyr", lib.loc="~/R/R-3.5.1/library")
 library("formattable", lib.loc="~/R/R-3.5.1/library")
library("DT", lib.loc="~/R/R-3.5.1/library")
```

```{r}
#Data invoegen
numberdata <- read_csv("D:/R-learning-curve/Selfmade exersizes/numberdata.csv")
#if there are NA's, this will remove it
numberdata <- drop_na(numberdata)
```

Now we have our data-set, we can use it for analysis and such.

The first package I wanted to use here was formatteble.
So lets import it and see what we can do.

```{r eval=FALSE, include=FALSE}
#lets first see the difference in showing the basic data
head(numberdata)
formattable(numberdata)
```

```{r}
#I like the 'formattable(numberdata)' better, however it will show all data (thats why I won't show it in this markdown)
# resolve this there is DT (package)
head(numberdata)
as.datatable(formattable(numberdata))
```

Woops, a little to much data.

Lets try to get some color in the data.

```{r}
as.datatable(formattable(numberdata, list(area(col = 2:5) ~ color_tile("transparent", "red"))))
```

Seems to work, but I would like some more colors.
Lets try again.

```{r}
as.datatable(formattable(numberdata, lapply(1:nrow(numberdata), function(row) {area(row, col = 2:5) ~ color_tile("red", "green")})))
```

That's what I wanted

I looked around for other formatting packages and fount 'kableExtra'. This one can be integrated with 'formattable', but can also work on its own. Lets try.

```{r eval=FALSE, include=FALSE}
#instal package
install.packages("kableExtra")
```


```{r}
#add library
library("knitr", lib.loc="~/R/R-3.5.1/library")
library("kableExtra", lib.loc="~/R/R-3.5.1/library")
library("dplyr", lib.loc="~/R/R-3.5.1/library")
library("dbplyr", lib.loc="~/R/R-3.5.1/library")
```

First I run the example code to see if it works and how it works.
Credits: https://haozhu233.github.io/kableExtra/use_kableExtra_with_formattable.html

```{r}
mtcars[1:5, 1:4] %>%
  mutate(
    car = row.names(.),
    mpg = color_tile("white", "orange")(mpg),
    cyl = cell_spec(cyl, "html", angle = (1:5)*60,
                    background = "red", color = "white", align = "center"),
    disp = ifelse(disp > 200,
                  cell_spec(disp, "html", color = "red", bold = T),
                  cell_spec(disp, "html", color = "green", italic = T)),
    hp = color_bar("lightgreen")(hp)
  ) %>%
  select(car, everything()) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(5, width = "3cm") %>%
  add_header_above(c(" ", "Hello" = 2, "World" = 2))
```

Let's see if I can do something with my own data-set, without crashing it.

```{r}
options(knitr.table.format = "html")
numberdata[, 1:5] %>%
  mutate(
    Open = cell_spec(numberdata$Open, "html", color = "red", background = ifelse(Open > (High - Low) / 2 +Low, "green", "blue")),
    Close = cell_spec(numberdata$Close, "html", color = "red", background = ifelse(Close > (High - Low) / 2 +Low, "green", "blue")),
    High = cell_spec(numberdata$High , "html",color = "black", background = ifelse(6 > High - Low, "lightgreen", "red"))
    ) %>%
  select(Date, Open, High, Low, Close) %>%
  kable(format = "html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  row_spec(0, angle = -45) %>%
  add_header_above(c(" " = 2, "Rates" = 2, "")) %>%
  add_header_above(c(" ", "Live" = 4)) %>%
  scroll_box(width = "100%", height = "300px")

```

That's the last thing I do with this. <br>

I like 'kableExtra' better than 'formattable', because it feels like I have more control over the data. Also 'kableExtra' is not as resource-heavy as 'formattable' (no warnings about to much dat). <br>

Switchs instead of ifelse would give me a lot more options
